### 2020-11-10 05_Thesis/THESIS_LaTeX/Chapters/1.tex
thesis match the template
references fix
thesis intro in progress

\begin{figure}[th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/CBNfingerprint.png}
\decoRule
\caption[CBN Fingerprint]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

Carbon is a versatile element capable to form a number of bonds with other elements or with itself. Cabon-based nano-materials (CBNs) exist in diverse forms, depending on the precise values of each degree of freedom that specify the material proclivity at multiple scales. Hybridization, crystallization, percolation, anisotropy, porosity, impurities and imperfections are some of the relevant features that determine the CBN set of properties. The combination of these features at the micro- and meso-scale burst a variety of macro-scale properties that comprise the CBN fingerprint (\ref{fig:CBNfingerprint}). The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids; and from black colour, bulks to transparent, disordered thin films. \cite{McCreery2008} Figure \ref{fig:carbonAllotropes} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/carbonAllotropes.png}
\decoRule
\caption[Carbon Allotropes]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
\label{fig:carbonAllotropes}
\end{figure}

Due to the versatility and variety of CBNs, CBNs have been fabricated and implemented for various purposes. \cite{Geim2011, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}. For instance, field effect transistors (FET) have been studied by Novoselov \cite{Novoselov2004} and Heersche et. al. \cite{Heersche2007}. Carbon FET devices have reported field-effect mobility one order of magnitude higher than that of silicon FETs. Other literature suggests CBNs to be favourable to detect a variety of gases and biomolecules. \cite{} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes.

%% Zhu2010

The properties of these CBNs make them widely used in many
fields ranging from material science [13, McCreery2008], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21]. Table 1 summarizes the main properties of the most common CBNs [22-25]:

Among the many carbon nanomaterials, CNTs and GR are currently the most popular representatives and have been extensively studied for their excellent mechanical strength, electrical and thermal conductivity and optical properties. The Young's modulus and tensile strength of CNTs and GR can reach 1 TPa and 130 GPa respectively [20,21]. Carrier mobility of graphene is around 860 $cm^{2} V^{-1} s^{-1}$ (hole mobility of 844 $cm^{2} V^{-1} s^{-1}$ and carrier mobility of 866 $cm^{2} V^{-1} s^{-1}$), and the current density of metallic CNTs is orders of magnitude higher than those of metals such as copper [26,27]. Thermal conductivities of CNTs and GR are about 3000e3500W/mK and 5000 W/mK respectively [28]. The light absorption ratio of single-layer graphene is limited to 2.5\% [29]. A large amount of the research efforts were focused on exploiting these properties for various applications including electronics, biological engineering, filtration, lightweight/strong composite materials, photovoltaic and energy storage [30-32]. CNTs and GR are naturally good electrical conductors and their biocompatibility can be modulated [33], making them good candidates for improving electrodes for neural interfaces. Electrical recording or stimulation of nerve cells is widely employed in neural prostheses (for hearing, vision, and limb-movement recovery), in clinical therapies (treating Parkinson's disease, dystonia, and chronic pain), as well as in basic neuroscience studies. In all these applications, electrodes of various shapes and dimensions stimulate and/or record neuronal activity to directly modulate behavior or to interface machine. The performance of the electrodes can be significantly improved by implementing the device with nanomaterial-based coatings (such as CBNs), since their high surface area can drastically increase charge injection capacity and decrease the interfacial impedance with neurons [34].

%%%
It is well known that the morphology of the electroactive material play an important role in electrochemical systems, once the intimate contact at the electrode/electrolyte interface is crucial to guarantee the charge transfer process [11,12]. In this sense, nanostructured electroactive materials such as nanorods [13], nanofiber [14], nanoflowers [15,16], nanowires [17,18], among others [19,20], are being widely used to obtain improved electrochemical properties such as higher charge/discharge rate and improved task to accommodate stress due to volume changes occasioned by intercalation process.

>>>>

\begin{figure}[th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process of Carbon Nano-wires]{Fabrication process and characterization techniques of conductive carbon nano-wires to achieve through the dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/CBNfingerprint.png}
\decoRule
\caption[Fingerprint of Carbon-based Nano-materials]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

Carbon is a versatile element capable to form a number of bonds with other elements or with itself. Cabon-based nano-materials (CBNs) exist in diverse forms, depending on the precise values of each degree of freedom that specify the material proclivity at multiple scales. Hybridization, crystallization, percolation, anisotropy, porosity, impurities and imperfections are some of the relevant features that determine the CBN set of properties. The combination of these features at the micro- and meso-scale burst a variety of macro-scale properties that comprise the CBN fingerprint (\ref{fig:CBNfingerprint}). The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids; and from black colour, bulks to transparent, disordered thin films. \cite{McCreery2008} Figures \ref{fig:carbonAllotropes} and \ref{fig:carbonAllotropesDiagram} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/carbonAllotropes.png}
\decoRule
\caption[Carbon sp-hybrid Nano-materials]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
\label{fig:carbonAllotropes}
\end{figure}

\begin{figure}[th]
\centering
\includegraphics[scale=0.80]{./Figures/carbonAllotropesHybridization.png}
\decoRule
\caption[Ternary Diagram of Carbon Allotropes based on sp Content]{Ternary phase diagram of amorphous carbon regions based on hybridization degree. Adapted from \cite{Heersche2007, Heimann1997, Belenkov2003, Fedel2013, Razeghi2019, AlstrupJensen2015}.}
\label{fig:carbonAllotropesDiagram}
\end{figure}

In terms of porosity, CBNs exhibit different properties according to the degree of 'open' and 'closed' pores. A 'closed pore' is a void or empty space in solid materials where a discontinuity is present within the array of atoms and molecules. On the other hand, an 'open pore' refers to a void which is connected to the outer surface of the solid, in other words a 'open pore' is a 'closed pore' with an opening to the external surface. \cite{Marsh1989} Figure \ref{fig:carbonAllotropesPorosityNOrder} shows a classification of carbon allotropes according to their porous content.

\begin{figure}[th]
\centering
\includegraphics[scale=0.80]{./Figures/carbonAllotropesPorosityNOrder.png}
\decoRule
\caption[Ternary Diagram of Carbon Allotropes based on Porosity and Structural Order]{Ternary phase diagram of amorphous carbon regions based on structure order and porosity. Regions are colored by the degree of crystalline order within the carbon structure. White represents highly ordered structures, whereas white represents disordered structures. \cite{Marsh1989, Hugh1994}}
\label{fig:carbonAllotropesPorosityNOrder}
\end{figure}

Thermal conductivity and electrical conductivity decrease with increasing porosity due to the reduced amount of material to conduct electrons and energy. Furthermore, porosity negatively affects the mechanical properties like strength and elastic modulus as it reduces the volume in which stresses are distributed. Moreover, stresses are concentrated at the pores which makes the material prone to mechanical failure. \cite{Marsh1989, Hugh1994}

Due to the versatility and variety of CBNs, CBNs have been fabricated and implemented for various purposes. \cite{Geim2011, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}. For instance, field effect transistors (FET) have been studied by Novoselov \cite{Novoselov2004} and Heersche et. al. \cite{Heersche2007}. Carbon FET devices have reported field-effect mobility one order of magnitude higher than that of silicon FETs. Other literature suggests CBNs to be favorable to detect a variety of gases and biomolecules. \cite{Schedin2007, Ohno2009} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes. Moreover, CBNs have showed good performace in applications in energy (prevent wastage of energy), water (purification) and diagnostics (lab-on-chip systems and nano-sensors). \cite{Cao2011, Khanna2016} As mentioned above, the morphology of CBNs has an impact on the electrochemical and mechanical properties. \cite{Marsh1989, Hugh1994, Guo2018} In this regard, carbon nano-structures, such as nano-wires \cite{Kundu2019, Bencheikh2019, Bencheikh2019}, have been fabricated to achieve improved electrochemical characteristics.

### 2020-11-10 05_Thesis/THESIS_LaTeX/main.tex
thesis intro in progress

%%----------------------------------------------------------------------------------------
%%	QUOTATION PAGE
%%----------------------------------------------------------------------------------------
%
%\vspace*{0.2\textheight}
%
%\begin{center}
%\includegraphics[width=0.60\textwidth]{./Figures/quote.png}
%
%\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
%\end{center}
%
%\begin{flushright}
%\textbf{Newton, Sir Isaac} \linebreak
%In W.I.B. Beveridge \linebreak
%\emph{The Art of Scientific Investigation} \linebreak
%Scientist (p. 145)
%\end{flushright}

>>>>

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{\fill}

\begin{center}
%\includegraphics[width=0.60\textwidth]{./Figures/quote.png}

\noindent\enquote{\itshape Carbon is a simple element but ............... \\
\medskip 
One branch of chemistry is devoted to its compounds! \\
\medskip 
One branch of science is devoted to the many forms of the element as a solid material. \\
\medskip 
The best of this is that although most carbon materials are grey or black to the naked eye and the uninitiated, a closer examination reveals the form, beauty and even color of carbon science.}\bigbreak
\end{center}

\begin{flushright}
\textbf{Marsh, Harry} \linebreak
\emph{Universitat d'Alacant, Alicante, Spain} \linebreak
\href{https://www.scopus.com/authid/detail.uri?authorId=7201585695}{scopus.com}
\end{flushright}

\vspace*{\fill}
